Concurrent Programming with CXL

### 2020-06-24 book/paper.tex
Making it easier to run test code

@@

We can run the code through CXL, but what would it test?  There are no
assert statements in the code.
We can split the functionality of this code into two pieces.  One is
the synchronization part: producers should never run more than \texttt{NSLOTS}
ahead of the consumers, but they should be able to produce up to \texttt{NSLOTS}
items even if there are no consumers.  The other part is the data: we want
to make sure that the items are sent through the buffer in order and without
loss.  We will first focus on the synchronization.

>>>>

\begin{figure}
\begin{code}
\VerbatimInput[xleftmargin=5mm,numbers=left]{code/BBsematest.cxl}
\end{code}
\caption{[BBsematest.cxl] Test program for Figure~\ref{fig:boundedbuffer}.}
\label{fig:bbtest}
\end{figure}

@@

Figure~\ref{fig:bbtest} invokes the code of Figure~\ref{fig:boundedbuffer}.
We can run this through CXL, but what would it test?  There are no
assert statements in the code.
We can split the functionality of this code into two pieces.  One is
the synchronization part: producers should never run more than \texttt{NSLOTS}
ahead of the consumers, but they should be able to produce up to \texttt{NSLOTS}
items even if there are no consumers.  The other part is the data: we want
to make sure that the items are sent through the buffer in order and without
loss.  We will first focus on the synchronization.
